Secure Composition of Robust and Optimising Compilers

### 2023-09-22 csf/main.tex
Text

This section presents the key meta-theoretic results of this paper concerning sequential compiler composition (and of optimisation passes) (\Cref{sec:sequential}) and concerning other kinds of compiler composition (\Cref{sec:other-compos}).
% and builds on prior work~\cite{kruse2022csc}\MK{mention this at all? may reveal identity even though its double-blind}. % MP: not needed at all, ever, workshop work does not need to be cited in the main work

@@

>>>>

This section presents the key meta-theoretic results of this paper concerning secure compiler compositions (\Cref{sec:sequential,sec:other-compos}).
Note that the presented framework works with arbitrary classes.
% and builds on prior work~\cite{kruse2022csc}\MK{mention this at all? may reveal identity even though its double-blind}. % MP: not needed at all, ever, workshop work does not need to be cited in the main work

@@

\textbf{Triviality.} Note that the theorem may give trivial results, i.e., the intersection of classes $\class[_1]$ and $\class[_2]$ may be empty. 
For example, consider $\rtp{\cc{\src{L}}{\trg{L}}}{\tmssafe}$ and $\rtp{\cc{\trg{L}}{\obj{L}}}{\smssafe}$, where $\cc{\trg{L}}{\obj{L}}$ introduces code that allocates a table that stores bounds information of pointers, but fails to insert code that deallocates this table.
By \Cref{def:trace:tmsdef}, this violates $\tmssafe$.
Therefore, no behavior resulting from programs produced by the $\cc{\trg{L}}{\obj{L}}$ compiler is secure with respect to $\tmssafe$, but only for $\smssafe$.
In turn, % TODO TODO TODO FIXME
